Evaluating Model Performances

### 2019-04-05 Scripts/evaluating_model_performances.Rmd
added to model performances script

figure <- ggarrange(p.g.ros,p.g.rus,p.g.smote,
                    p.k.ros,p.k.rus,p.k.smote,ncol = 3, nrow = 2, common.legend = TRUE, legend = "top")
figure
annotate_figure(figure,
    bottom = text_grob("Resampling Technique", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)

>>>>

figure <- ggarrange(p.g.none,p.g.none,
                p.g.ros,p.k.ros,
                p.g.rus,p.k.rus,
                p.g.smote,p.k.smote,
                ncol = 2, nrow = 4, 
                common.legend = TRUE, 
                legend = "top",
                labels = c("A","",
                           "B","",
                           "C","",
                           "D",""),
                font.label = list(size=20))
figure
annotate_figure(figure,
    bottom = text_grob("Resampling Technique", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)
